---
title: "01_Get_annual_data"
author: "DHJ"
date: "4 11 2019"
output: 
  html_document:
    keep_md: true
    toc: true
    toc_float: true
---
    
*Air temperature and precipitation for a bunch of stations*    
* Part 1- Username  
* Parts 2-3 - Get annual mean air temperature and precipitation for a bunch of stations and perform Theil-Sen regression
* Part 4 - Find stations on interactive map  
* Part 5 - Get monthly data
    
Technically:  
* Based on examples from https://frost.met.no/ex_userquest  
* NOTE: Some nice function for finding stations in part 4  
* Also see https://github.com/metno/gibson and https://github.com/metno/esd 
(not used here, tested elsewhere)
   
Also see station map here: http://eklima.met.no/Help/Stations/toDay/all/no_Stations.html  
   
**Important note:** for monthly data (part 5), there are two offsets for each series: PT0H and PT6H. Which to use?  
- For precipitation "sum(precipitation_amount P1M)", we use PT6H	(standard sampling period for precipitation is 07-06 UTC)  
- For temperature "mean(air_temperature P1M)", we use PT0H	 
Source: https://frost.met.no/dataclarifications.html 


## Years  
```{r}
year1 <- 1980
year2 <- 2019

```


## 0. Libraries  
```{r setup, include=FALSE}
# install.packages("bitops")
# install.packages("RCurl")
# install.packages("rkt")
library(RCurl)      # Downloading from ftp using getURL()
library(jsonlite)   # Handling json
library(dplyr)      # Functions %>%, group_by(), summarise() and more
library(purrr)      # Function map()
library(lubridate)  # Functions year(), month(), ymd_hms(), ymd()
library(rkt)        # Theil -Sen Regression

source("01fun_Get_annual_data.R")
source("01_Password.R")

# Not really necessary
library(ggplot2)    # Plotting

```

## 1. Username
Stores your username in an object we call 'opts' (is used later)
* How to get username - see   
   https://frost.met.no/concepts#getting_started

```{r}

opts <- curlOptions(
  userpwd = txt_pwd, 
  ftp.filemethod = "singlecwd")

```


## 2. Example station: Melsom   

### a. Station identifier
```{r}
stid <- "SN18700"
```


### b. Avaliable series

```{r}
df_info <- get_series_from_station(stid)
# View(df_info)
head(df_info)

```

#### b1. Available time resolutions - from 1 hour (PT1H) to 1 year (P1Y)
```{r}
table(df_info$timeResolution)
```

#### b2. Available year-level series  
```{r}
subset(df_info, timeResolution == "P1Y")$elementId

```

### c. Get temperature data from Oslo Blindern
```{r}
# year1, year2, parameter, station
# debugonce(get_data)
# debugonce(get_data_i)
df <- get_data(year1, year2, "mean(air_temperature P1Y)", "SN18700")
head(df)
```

### d. Note: One can also get data for several stations at once!  
This could be utilized in part 2 (but it is not)
```{r}
df <- get_data(year1, year2, "mean(air_temperature P1Y)", "SN18700,SN50540")
head(df)
```

### e. Theil-Sen regression using function  
```{r}
a <- get_theil_sen(year1, year2, "mean(air_temperature P1Y)", "SN27450")
b <- get_theil_sen(year1, year2, "sum(precipitation_amount P1Y)", "SN18700")

bind_rows(a$statistics, b$statistics)
```


## 3. Get trends    
See part 4 for how to find stations

### a. Temperature
```{r}
x <- c(700,18700,19710,27470,27470,36560,39040,44560,44560,46910,52290,
       58070,64550,69100,69100,85380,89350,93140,96800,99370)
stations_temp <- paste0("SN", x)

get_theil_sen_safe <- safely(get_theil_sen)  # generates a list with $result and $error

result_list1 <- stations_temp %>% map(~get_theil_sen_safe(year1, year2, "mean(air_temperature P1Y)", .))
not_ok <- result_list1 %>% map_lgl(is.null)
mean(not_ok)   # Should be zero!

result_list2 <- transpose(result_list1)$result  # Go down to 1st level of list
result_temp <- transpose(result_list2)$statistics %>% bind_rows()  # Go down to 1st level of list

# df_temp <- stations_temp[1:2] %>% map_df(~get_theil_sen(year1, year2, "mean(air_temperature P1Y)", .))
result_temp

```

#### Plot  
```{r}
data_plot <- transpose(result_list2)$data %>% bind_rows()

# data_plot

ggplot(data_plot, aes(Year, value)) +
  geom_smooth(method = "lm") +
  geom_point() +
  facet_wrap(vars(Station), scales = "free_y")

```

### b. Precipitation
```{r}
x <- c(3780,18700,19710,30000,30260,36560,39040,43360,44080,
       46850,51250,57480,63530,66210,68270,78850,89350,93140,96970,99500)

stations_prec <- paste0("SN", x)

result_list1 <- stations_prec %>% map(~get_theil_sen_safe(year1, year2, "sum(precipitation_amount P1Y)", .))
not_ok <- result_list1 %>% map_lgl(is.null)
mean(not_ok)   # Should be zero!

result_list2 <- transpose(result_list1)$result  # Go down to 1st level of list
result_prec <- transpose(result_list2)$result %>% bind_rows()

result_prec

```

#### Plot  
```{r}
data_plot <- transpose(result_list2)$data %>% bind_rows()

# data_plot

ggplot(data_plot, aes(Year, value)) +
  geom_smooth(method = "lm") +
  geom_point() +
  facet_wrap(vars(Station), scales = "free_y")


```

### c. Save  
```{r}
res <- list(Temperature = result_temp, Precipitation = result_prec)

openxlsx::write.xlsx(
  res, 
  paste0(
    "Data/Elevoverv_trends_climate_", year1, "-", year2, ".xlsx (script 01).xlsx"
    )
)

```


## 4. Check available stations  

### a. Check available temperature series  
Overlapping wholly or partly with this period
```{r}
df <- get_station_from_parameter("mean(air_temperature P1Y)", 2016, 2017)
head(df)
```

### b. Get information on station, incl. coordinates  
```{r}
# A single string
df_station <- get_station_meta("SN44190,SN27450")
df_station

# A vector of strings
df_station <- get_station_meta(c("SN44190","SN27450"))
df_station

# A vector of strings, including ":0"
df_station <- get_station_meta(c("SN31660:0", "SN40250:0"))
df_station

# Feed it with the output of previous chunk. Note that only "SN" stations are used
df_station <- get_station_meta(df$sourceId)
nrow(df_station)

```


### c. Show one station on Norgeskart

```{r}
if (interactive()){
  show_norgeskart(df_station, 1)   # station number one in file
  # OR vector
  show_norgeskart(c(60, 11))
  # OR two values
  show_norgeskart(60, 11)
}
```

### d. Show stations on leaflet map

```{r}

library(leaflet)

df_station <- df_station %>%
  mutate(Popuptext = 
           paste0(id, "<BR>",
                  "<B>", shortName, "</B><BR>",
                  "M.a.s.l. = ", masl, "<BR>",
                  "valid from = ", validFrom, "<BR>",
                  "Coor.: ", round(Long, 4), ", ", round(Lat, 4))
         )

leaflet() %>%
  addTiles() %>%
  addMarkers(lng = df_station$Long, lat = df_station$Lat,
             popup = df_station$Popuptext)

```


## 5. Get monthly data for last year  
For year2, or earlier if data stops earlier  

### a. Available month-level series  
```{r}
subset(df_info, timeResolution == "P1M" & grepl("temp", elementId))$elementId
#  "mean(air_temperature P1M)"
subset(df_info, timeResolution == "P1M" & grepl("prec", elementId))$elementId
#  "sum(precipitation_amount P1M)" 

```
### b. Test   
Not offsets used. See "important note" at top of this document  
```{r}
# test
if (FALSE){
  get_data(year2, year2, "mean(air_temperature P1M)", "SN18700") %>%
    filter(timeOffset == "PT0H")
  
  get_data_safe <- safely(get_data)
  
  x <- c(700,18700,19710,27470,27470,36560,39040,44560,44560,46910,52290,
         58070,64550,69100,69100,85380,89350,93140,96800,99370)
  stations_temp <- paste0("SN", x)
  
  data_list <- stations_temp %>% 
    map(~get_data_safe(year2, year2, "mean(air_temperature P1M)", .))
  # Which ones are without error?
  ok <- data_list %>% map_lgl(~is.null(.$error))
  
  data_temp <- transpose(data_list[ok])$result %>%     # Get "result" from those that are ok
    bind_rows() %>%
    filter(timeOffset == "PT0H") %>%                   # We want this offset (see comment on offsets)
    mutate(Station = sub(":0", "", sourceId, fixed = TRUE))
  
  # Check data
  ggplot(data_temp, aes(referenceTime, value)) +
    geom_point() + geom_line() +
    facet_wrap(vars(Station))
  
}

```


### c. Function  
```{r}
#
# Get monthly data for years given
#
get_monthly_data <- function(...){
  result <- get_data(...)
  if (grepl("precipitation", result$elementId[1])){
    result <- result %>%
      filter(timeOffset == "PT6H")
  } else {
    result <- result %>%
      filter(timeOffset == "PT0H")
  }
  result <- result %>%
    mutate(Station = sub(":0", "", sourceId, fixed = TRUE),
           Year = lubridate::year(referenceTime),
           Month = lubridate::month(referenceTime)) %>%
    select(Station, Parameter, Year, Month, value,	unit,
           timeOffset,	timeResolution,	timeSeriesId,	
           performanceCategory,	exposureCategory,	qualityCode)
  result
  }

#
# Get monthly data for last "full" year given
#
get_monthly_data_lastyear <- function(...){
  result <- get_monthly_data(...)
  last_year <- result %>%
    count(Year) %>%
    filter(n %in% 12) %>%
    tail(1) %>%
    pull(Year)
  result %>%
    filter(Year %in% last_year)
}

get_monthly_data_lastyear_safe <- safely(get_monthly_data_lastyear)

# test
if (FALSE){
  get_monthly_data(year2, year2, "mean(air_temperature P1M)", "SN18700")
  get_monthly_data_lastyear(year2-10, year2, "mean(air_temperature P1M)", "SN18700")
  get_monthly_data_lastyear(year2-10, year2, "sum(precipitation_amount P1M)", "SN30260")
  }
```


### d. Temperature  
Last year for each station (given they have data at least after 1998)   
```{r}

x <- c(700,18700,19710,27470,27470,36560,39040,44560,44560,46910,52290,
       58070,64550,69100,69100,85380,89350,93140,96800,99370)
stations <- paste0("SN", x)

data_list <- stations %>% 
  map(~get_monthly_data_lastyear_safe(1998, year2, "mean(air_temperature P1M)", .))

# Which ones are without error?
ok <- data_list %>% map_lgl(~is.null(.$error))
  
data_temp <- transpose(data_list[ok])$result %>%     # Get "result" from those that are ok
  bind_rows()

# Check data
ggplot(data_temp, aes(Month, value)) +
  geom_point() + geom_line() +
  facet_wrap(vars(Station))


```

### e. Precipitation   
Last year for each station (given they have data at least after 1998)   
```{r}
x <- c(3780,18700,19710,30000,30260,36560,39040,43360,44080,
       46850,51250,57480,63530,66210,68270,78850,89350,93140,96970,99500)
stations <- paste0("SN", x)

data_list <- stations %>% 
  map(~get_monthly_data_lastyear_safe(1998, year2, "sum(precipitation_amount P1M)", .))

# Which ones are without error?
ok <- data_list %>% map_lgl(~is.null(.$error))
  
data_prec <- transpose(data_list[ok])$result %>%     # Get "result" from those that are ok
  bind_rows()

# Check data
ggplot(data_prec, aes(Month, value)) +
  geom_point() + geom_line() +
  facet_wrap(vars(Station))


```

### f. Save
```{r}

openxlsx::write.xlsx(
  list(Temperature = data_temp, Precipitation = data_prec),
  paste0("Data/Monthly temp and prec in last year with data - ", year2, " (script 01).xlsx")
)
  

```



