---
title: "02_Collect_data"
author: "DHJ"
date: "30 9 2020"
output: html_document
---

Extract surface and 4-5 temperature for Dk1 (Steilene) in Indre Oslofjord.   
  
Note: this script utilizes data from project "Oslofjord_indre". Both these data and the results form this script have been put here:  
K:/Avdeling/214-Oseanografi/DHJ/Data/Oslofjord_indre  
  


## 1. Libraries  
```{r}

library(dplyr)
library(readxl)
library(lubridate)
library(purrr)
library(tidyr)
library(viridis)

```

## 2. Read data from project "Oslofjord_indre"  
```{r}

fn <- "K:/Avdeling/214-Oseanografi/DHJ/Data/Oslofjord_indre/Indre_Oslofjord_temp_salt_1933-2019.rds"
dat <- readRDS(fn)

cat("dat:", nrow(dat), "lines \n")

```
### Check data   
Last date is 2019-08-24  
```{r}

xtabs(~year(Date), dat)

xtabs(~Date + Station, dat %>% filter(year(Date) == 2019))

```


## 3. Check whether there are newer data    
CDT files prepared by André   
Turns out this has no newer data    
```{r}

#
# Code from script 34 in project "Oslofjord_indre"   (section 4 data 'd')
#

folder <- "K:/Avdeling/214-Oseanografi/DATABASER/OKOKYST_2017/IO_2019_2023/xlsbase_IO"
files <- dir(folder)
files <- files[!substr(files,1,1) == "~"]
files <- files[!files %in% c("IO2019_CTD_uferdig.xlsm", "notes.txt", "Thumbs.db", "Til_Aquamonitor")]
files
names(files) <- files

# Read all files, saved as list (ca 10 seconds)
dat_xl_list <- files %>% purrr::map(~readxl::read_excel(paste0(folder, "/", .), sheet = "nc"))

# Check column names
# dat_xl_list %>% map(names)

# Check StationId
# dat_xl_list %>% map(~xtabs(~StationId, .))

# In file Gp2_CTD_2019.xlsx, StationId = Gp1
# We correct this:
dat_xl_list[["Gp2_CTD_2019.xlsx"]]$StationId <- "Gp2"

# Column names ok - we combine to a single data frame
dat_xl <- bind_rows(dat_xl_list)

# str(dat_xl)

df_d <- dat_xl %>%
  mutate(Time = as.POSIXct((Date - 25569)*24*3600, origin = "1970-01-01", tz = "GMT"),
         Date = round_date(Time, "day") %>% as.Date(),
         Depth = (Depth1 + Depth2)/2
         ) %>%
  rename(Station = StationId,
         Temperature = Temperatur,
         Salinity = Saltholdighet) %>%
  select(Station, Date, Depth, Temperature, Salinity) %>%
  mutate(Source = "NIVA excel 2019")
  
xtabs(~Date + Station, df_d)

```
## 4. Dk1 temperature {.tabset} 

### Depths  
```{r}

dat %>%
  filter(Depth <= 15) %>%
  ggplot(aes(Date, Depth, color = Source)) +
  geom_point()

```


### Surface (0-1 m)  
```{r}

gg <- dat %>%
  filter(Depth <= 1 & Station == "Dk1") %>%
  arrange(Date) %>%
  mutate(Source = forcats::fct_inorder(Source),
         Depth = factor(Depth)) %>%
  ggplot(aes(Date, Temperature, color = Depth, linetype = Depth)) +
  geom_line()
gg + 
  facet_grid(rows = vars(Source))

```
### 4-5 m    
```{r}

gg <- dat %>%
  filter(Depth >= 4 & Depth <= 5.5 & Station == "Dk1") %>%
  arrange(Date) %>%
  mutate(Source = forcats::fct_inorder(Source),
         Depth = factor(Depth)) %>%
  ggplot(aes(Date, Temperature, color = factor(Depth), linetype = factor(Depth))) +
  geom_line()
gg + 
  facet_grid(rows = vars(Source))

```
## 5. Pick Dk1 surface + 5 m data   

### Surface  
* Through 2009: 0 m only   
* 2010-2012: 0.5 m, plus sometimes 1 m. Pick 0.5 m  
* 2013-2018: 1.0 m, plus sometimes 0.5 m. Pick 1 m  
* 2019: 0.25 m + 1 m. Pick 0.25 m      
```{r}

dk1_surface <- dat %>%
  filter(Depth <= 1 & Station == "Dk1") %>%
  select(Date, Depth, Temperature) %>%
  tidyr::pivot_wider(names_from = "Depth", values_from = "Temperature")

if (FALSE){
  View(dk1_surface %>% filter(year(Date) >= 2008))
}

dk1_surface <- dk1_surface %>%
  mutate(
    Temp_surface = case_when(
      year(Date) <= 2009 ~ `0`,
      year(Date) <= 2012 ~ `0.5`,
      year(Date) <= 2018 ~ `1`,
      year(Date) <= 2019 ~ `0.25`),
    Depth_surface = case_when(
      year(Date) <= 2009 ~ 0,
      year(Date) <= 2012 ~ 0.5,
      year(Date) <= 2018 ~ 1,
      year(Date) <= 2019 ~ 0.25)
    )

cat("dk1_surface:", nrow(dk1_surface), "lines \n")

```
### 4-5 m    
* Through 1960: 5 m only   
* 1962-2012: 4 m, plus sometimes 5 m. Pick 4 m   
* 2013-2014: Both 4 and 5 m. Pick 5 m   
* 2015-2019: 5 m, plus sometimes 4 m. Pick 5 m   
```{r}

dk1_4to5m <- dat %>%
  filter(Depth >= 4 & Depth <= 5.5 & Station == "Dk1") %>%
  select(Date, Depth, Temperature) %>%
  tidyr::pivot_wider(names_from = "Depth", values_from = "Temperature")

if (FALSE){
  View(dk1_4to5m %>% filter(year(Date) %in% 1960:1965))
  View(dk1_4to5m %>% filter(year(Date) %in% 2010:2020))
}

dk1_4to5m <- dk1_4to5m %>%
  mutate(
    Temp_4to5 = case_when(
      year(Date) <= 1961 ~ `5`,
      year(Date) <= 2012 ~ `4`,
      year(Date) <= 2019 ~ `5`),
    Depth_4to5 = case_when(
      year(Date) <= 1961 ~ 5,
      year(Date) <= 2012 ~ 4,
      year(Date) <= 2019 ~ 5)
    )

cat("dk1_4to5m:", nrow(dk1_4to5m), "lines \n")

```



### Combine  

```{r}

dk1_temp_0to5meter <- full_join(dk1_surface, dk1_4to5m, by = "Date") %>%
  mutate(Year = year(Date),
         Month = month(Date))

cat("dk1_temp_0to5meter:", nrow(dk1_temp_0to5meter), "lines \n")

```


## 6. Plot {.tabset}  

### 5 m vs surface  
```{r}
ggplot(dk1_temp_0to5meter, aes(Temp_surface, Temp_4to5, color = Year)) +
  geom_point() +
  scale_color_viridis() +
  geom_abline(intercept = 0, slope = 1)

```

### 5 m vs surface by month  
```{r}
ggplot(dk1_temp_0to5meter, aes(Temp_surface, Temp_4to5, color = Year)) +
  geom_point() +
  scale_color_viridis() +
  geom_abline(intercept = 0, slope = 1) +
  facet_wrap(vars(Month))

```

### Time series
```{r, fig.width=9}
dk1_temp_0to5meter_long <- dk1_temp_0to5meter %>%
  select(Date, Year, Month, Temp_surface, Temp_4to5) %>%
  tidyr::pivot_longer(c(Temp_surface, Temp_4to5), names_to = "Depth", values_to = "Temperature")
  
ggplot(dk1_temp_0to5meter_long, aes(Date, Temperature, color = Depth)) +
  geom_point() +
  geom_line()

```

### Time series by month  
```{r, fig.width=9}

ggplot(dk1_temp_0to5meter_long, aes(Date, Temperature, color = Depth)) +
  geom_smooth(method = "lm", formula = 'y ~ x') +
  geom_point() +
  facet_wrap(vars(Month), labeller = "label_both")

```
## 7. Save  
```{r}

saveRDS(dk1_temp_0to5meter, "Data/dk1_temp_0to5meter.rds")
saveRDS(dk1_temp_0to5meter_long, "Data/dk1_temp_0to5meter_long.rds")


notes_for_excel <- tribble(
  ~ Notes,
  "Surface data are frpom depth 0, 0.25, 0.5 and/or 1 m",
  "Temp_surface gives temperature at one of these depths (Depth_surface gives the depth used for each line)",
  "Same for Temp_4to5 (depth at 4 or 5 m depth)",
  NA,
  "Rules used for surface:",
  "* Through 2009: 0 m only",   
  "* 2010-2012: 0.5 m, plus sometimes 1 m. Pick 0.5 m",  
  "* 2013-2018: 1.0 m, plus sometimes 0.5 m. Pick 1 m",  
  "* 2019: 0.25 m + 1 m. Pick 0.25 m", 
  NA,
  "Rules used for 4-5 m:",
  "* Through 1960: 5 m only",   
  "* 1962-2012: 4 m, plus sometimes 5 m. Pick 4 m",   
  "* 2013-2014: Both 4 and 5 m. Pick 5 m",   
  "* 2015-2019: 5 m, plus sometimes 4 m. Pick 5 m",
  NA,
  "These data are based on",
  "K:/Avdeling/214-Oseanografi/DHJ/Data/Oslofjord_indre/Indre_Oslofjord_temp_salt_1933-2019.rds",
  "and were produced by DHJ using",
  "C:/Data/Various-R/Annette_temp_DK1/02_Collect_data.Rmd"
)

list(
  data = dk1_temp_0to5meter,
  notes = notes_for_excel
  ) %>%
  writexl::write_xlsx("Data/dk1_temp_0to5meter.xlsx")

list(
  data = dk1_temp_0to5meter_long,
  notes = notes_for_excel
  ) %>%
  writexl::write_xlsx("Data/dk1_temp_0to5meter_long.xlsx")

```

